SDR enhancement by clouds

### 2024-04-01 article/article.Rmd
Commit 2024-04-01 13:13

The shortwave solar irradiance, reaches the Earth's surface, is the main energy
source of the atmosphere and biosphere. It drives and governs the climate
[@Gray2010].  It has direct practical application, in different industries, like
energy production and agriculture method.  The variability of its intensity, can
cause difficulties in predicting the yield and designing the appropriate equipment.
A lot of research focus on predicting the renewable energy production in a  very fine
timescale and in near real-time (for a review see @Inman2013; @Graabak2016).

A big aspect of this variability are the interaction with the clouds. In general,
clouds absorb part of the solar irradiance, but under certain conditions, can
enhance the total shortwave irradiance reaching the ground. This effect can locally
increase the observed total shortwave irradiance higher than the expected clear sky
irradiance [see references therein].
.... cite ....
Those enhancements have been reported to be able to exceed .... and duration.
And in extreme cases can compromise the integrity of the infrastructure.
.... cite ....
@Martins2022

>>>>

The shortwave solar irradiance, reaches the Earth's surface, is the main energy
source of the atmosphere and biosphere. It drives and governs the climate
[@Gray2010].  It has direct practical application, in different industries, like
energy production and agriculture method.  The variability of its intensity, can
cause difficulties in predicting the yield and designing the appropriate equipment.
A lot of research has been focuces on predicting the renewable energy production in a fine
timescale and in near real-time (for a review see @Inman2013; @Graabak2016).

A big aspect of this variability are the interaction with the clouds. In general,
clouds absorb part of the solar irradiance, but under certain conditions, can
enhance the total shortwave irradiance reaching the ground. This effect can locally
increase the observed total shortwave irradiance higher than the expected clear sky
irradiance [see references therein].

The enhancements can effect the efficiency and stability of photovoltaic power
production [@Lappalainen2020; @Jaervelae2020].

And extreme enhancements cases have the potential to  compromise the integrity of the
infrastructure  [@DoNascimento2019].

Those enhancements have been reported to be able to exceed .... and duration.
For a list of recorded extreme cases
@Martins2022

### 2024-04-01 article/article.tex
Commit 2024-04-01 13:13

The shortwave solar irradiance, reaches the Earth's surface, is the main energy
source of the atmosphere and biosphere. It drives and governs the climate
(Gray et al. 2010). It has direct practical application, in different industries, like
energy production and agriculture method. The variability of its intensity, can
cause difficulties in predicting the yield and designing the appropriate equipment.
A lot of research focus on predicting the renewable energy production in a very fine
timescale and in near real-time (for a review see Inman, Pedro, and Coimbra (2013); Graabak and Korpås (2016)).

A big aspect of this variability are the interaction with the clouds. In general,
clouds absorb part of the solar irradiance, but under certain conditions, can
enhance the total shortwave irradiance reaching the ground. This effect can locally
increase the observed total shortwave irradiance higher than the expected clear sky
irradiance {[}see references therein{]}.
\ldots. cite \ldots.
Those enhancements have been reported to be able to exceed \ldots. and duration.
And in extreme cases can compromise the integrity of the infrastructure.
\ldots. cite \ldots.
Martins, Mantelli, and Rüther (2022)

@@

@@

@@

>>>>

The shortwave solar irradiance, reaches the Earth's surface, is the main energy
source of the atmosphere and biosphere. It drives and governs the climate
(Gray et al. 2010). It has direct practical application, in different industries, like
energy production and agriculture method. The variability of its intensity, can
cause difficulties in predicting the yield and designing the appropriate equipment.
A lot of research has been focuces on predicting the renewable energy production in a fine
timescale and in near real-time (for a review see Inman, Pedro, and Coimbra (2013); Graabak and Korpås (2016)).

A big aspect of this variability are the interaction with the clouds. In general,
clouds absorb part of the solar irradiance, but under certain conditions, can
enhance the total shortwave irradiance reaching the ground. This effect can locally
increase the observed total shortwave irradiance higher than the expected clear sky
irradiance {[}see references therein{]}.

The enhancements can effect the efficiency and stability of photovoltaic power
production (Lappalainen and Kleissl 2020; Järvelä and Valkealahti 2020).

And extreme enhancements cases have the potential to compromise the integrity of the
infrastructure (Do Nascimento et al. 2019).

Those enhancements have been reported to be able to exceed \ldots. and duration.
For a list of recorded extreme cases
Martins, Mantelli, and Rüther (2022)

@@

\leavevmode\vadjust pre{\hypertarget{ref-DoNascimento2019}{}}%
Do Nascimento, Lucas Rafael, Trajano De Souza Viana, Rafael Antunes Campos, and Ricardo Rüther. 2019. {``Extreme Solar Overirradiance Events: Occurrence and Impacts on Utility-Scale Photovoltaic Power Plants in Brazil.''} \emph{Solar Energy} 186 (July): 370--81. \url{https://doi.org/10.1016/j.solener.2019.05.008}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Jaervelae2020}{}}%
Järvelä, Markku, and Seppo Valkealahti. 2020. {``Operation of a {PV} Power Plant During Overpower Events Caused by the Cloud Enhancement Phenomenon.''} \emph{Energies} 13 (9): 2185. \url{https://doi.org/10.3390/en13092185}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Lappalainen2020}{}}%
Lappalainen, Kari, and Jan Kleissl. 2020. {``Analysis of the Cloud Enhancement Phenomenon and Its Effects on Photovoltaic Generators Based on Cloud Speed Sensor Measurements.''} \emph{Journal of Renewable and Sustainable Energy} 12 (4): 043502. \url{https://doi.org/10.1063/5.0007550}.
